Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-10-29 Tex/Old text/chapters/appendixB.tex
revised appendix B
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\section{Tools}

During the PhD process, the techniques from computer science and proposed to tackle issues related to solar photovoltaic systems became algorithms and codes. Those codes became tools, and the tools were used during comparative with simulation tool in order to validate the techniques.

In general, we pursuit to write code that could be verification tool independent, i.e., that can be used in any model checking tool without adaptation, since that we aimed to evaluate different .

We wrote the tools in Language C, without the use of '\# include', or '\# define'. Based on the fact that there is no use of compiler library, it was necessary to write some functions which perform specific calculations according to the adopted mathematical models (logarithm of natural order and exponential).

\subsection{Automated Verification Tool (PV System validation)}
\label{sec:automatedverification}

The code can be divided in four blocks:

\begin{itemize}
\item \textbf{Block 1}: global variables declaration, with weather data from location (minimum and maximum solar irradiance and temperature, for 24-hour of the day) as array, requirements, and data sheet information from each equipment of the PV system that will be verified;

\item \textbf{Block 2}: support functions (logarithm of natural order, exponential);

@@

\item \textbf{Block 4}: main code with charge, discharge battery control, based on PV generation from solar panels and the state of charge form batteries, having the commitment to deliver the power and energy that the house demands, according with the restrictions form the sized system.
\end{itemize}

\subsection{Automated Synthesis Tool (PV System Optimal Sizing)}
\label{sec:automatedsynthesis}

The code can be divided in three blocks:

\begin{itemize}
\item \textbf{Block 1}: global variables declaration, with weather data from location, requirements, and data sheet information from each equipment of the PV system that will be verified;

\item \textbf{Block 2}: support functions (start value with lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions with model checking);

@@

\section{How to use it}

The only block that demands user intervention from user in order to input data is the block 1 of both tools. If it is aimed to change the mathematical model adopted, so coding must be done in block 3 of automated verification tool and in block 2 of automated synthesis tool.

@@

\begin{itemize}
\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location;
\item Minimum and maximum temperature (average for every month of the year);
\item Local insolation (average number of sun hours by day at the location);
\item Number of solar panels in series;
\item Number of solar panels in parallel;
\item Number of series-connected cells from each solar panel;
\item Nominal Operating Cell Temperature;
\item Reference solar irradiance;
\item Reference temperature;
\item Short-circuit current temperature coefficient;
\item Open-circuit voltage temperature coefficient;
\item Reference short-circuit current;
\item Reference open-circuit voltage;
\item Reference maximum current, voltage, and power;
\item Minimum MPPT voltage;
\item Operation current;
\item Solar panel efficiency;
\item Panel area in square meters;
\item DC-bus voltage;
\item Individual battery voltage;
\item Battery bank capacity;
\item State of charge limit;
\item Number of batteries in series;
\item Number of batteries in parallel;
\item Autonomy of the batteries;
\item Efficiency from batteries;
\item Float, absorption and bulk battery voltages;
\item Charge controller efficiency;
\item Charge controller current;
\item Charge controller maximum voltage;
\item Inverter output voltage;
\item Inverter AC reference power;
\item Inverter maximum (surge) AC power reference;
\item AC voltage (outlet standard);
\item Power demand from the house;
\item Surge demand from the house;
\item Energy consumption from the house.
\end{itemize}

And regarding the automated synthesis tool, it is necessary the following data (editing and modifying the code):

@@

\subsection{Automated Verification with Incremental ESBMC}

Here we describe specifically how to use the code explained in previous section (\ref{sec:automatedverification}) using the incremental ESBMC with Z3 solver, that presented the better performance during the comparative with other verifiers. However, in \ref{sec:setup} it was showed how to use the code with other verifiers.

@@

Some results issued by the ESBMC verifier were depicted in \ref{sec:ESBMCverification} when performing the case studies.

\subsection{Automated Synthesis with CPAchecker}

Here we describe specifically how to use the code explained in previous sections (\ref{sec:automatedsynthesis}) using CPAchecker with MathSAT solver, that presented the better performance during the comparative with other verifiers. However, in \ref{sec:synthesissetup} it was showed how to use the code with other verifiers.

@@

Install a Java Runtime Environment which is at least Java 8 compatible (e.g., Oracle JRE, OpenJDK). Cf. the web site \url{http://java.oracle.com/}.

@@

Worth to mention that the default heap size is 1200m (or 1.2 GB of RAM), however it is indicated to specify a large value with '-heap' if you have more RAM memory available. In our case, we adjusted the heap to 64000m (64 GB).

Other important issue is the time-out of the execution process: the parameter 'limits.time.cpu' at the file 'resource-limits.properties' in folder 'config/includes' must be edited according the desired value. In our case, 'limits.time.cpu = 14400s', i.e., 14400 seconds or 240 minutes or 4 hours.

Some results, reports and graphics, issued by the CPAchecker verifier were depicted in \ref{sec:synthesisresults}.

>>>>

%---------------------------------------
\section{Tools}
%---------------------------------------

During the Ph.D. process, the techniques from computer science proposed to tackle issues related to solar photovoltaic systems became algorithms and programs. Those programs became tools, and the tools were used during comparative with simulation tools in order to validate the techniques.

\textcolor{red}{the second part of this sentence is unclear...} In general, we pursuit to write code that could be verification tool independent, i.e., that can be used in any model checking tool without adaptation, since we aimed to evaluate different.

We wrote the tools in the C programming language, without the use of '\# include', or '\# define'. Based on the fact that there exists no use of compiler library, it was necessary to write some functions, which perform specific calculations according to the adopted mathematical models (e.g., logarithm of natural order and exponential).

%---------------------------------------
\subsection{Automated Verification Tool (PV System validation)}
\label{sec:automatedverification}
%---------------------------------------

We split the code into four blocks:

\begin{itemize}
\item \textbf{Block 1}: global variables declaration, with weather data from location (minimum and maximum solar irradiance and temperature, for 24-hour of the day) as array, requirements, and datasheet information from each equipment of the PV system that will be verified;

\item \textbf{Block 2}: support functions (e.g., logarithm of natural order, exponential);

@@

\item \textbf{Block 4}: main code with charge, discharge battery control, based on PV generation from solar panels and the state of charge form batteries, committing to deliver the power and energy that the house demands, according with the restrictions form the sized system.
\end{itemize}

%---------------------------------------
\subsection{Automated Synthesis Tool (PV System Optimal Sizing)}
\label{sec:automatedsynthesis}
%---------------------------------------

We split the code into three blocks:

\begin{itemize}
\item \textbf{Block 1}: global variables declaration, with weather data from location, requirements, and datasheet information from each equipment of the PV system that will be verified;

\item \textbf{Block 2}: support functions (start value with the lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions with model checking);

@@

%---------------------------------------
\section{How to use it}
%---------------------------------------

The only block that demands user intervention to input data is block 1 of both tools \textcolor{red}{where can I see block 1? which tools?}. If it is aimed to change the mathematical model adopted, so coding must be done in block 3 of the automated verification tool and block 2 of the automated synthesis tool.

@@

\begin{itemize}
\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location;
\item Minimum and maximum temperature (average for every month of the year);
\item Local insolation (average number of sun hours by day at the location);
\item Number of solar panels in series;
\item Number of solar panels in parallel;
\item Number of series-connected cells from each solar panel;
\item Nominal Operating Cell Temperature;
\item Reference solar irradiance;
\item Reference temperature;
\item Short-circuit current temperature coefficient;
\item Open-circuit voltage temperature coefficient;
\item Reference short-circuit current;
\item Reference open-circuit voltage;
\item Reference maximum current, voltage, and power;
\item Minimum MPPT voltage;
\item Operation current;
\item Solar panel efficiency;
\item Panel area in square meters;
\item DC-bus voltage;
\item Individual battery voltage;
\item Battery bank capacity;
\item State of charge limit;
\item Number of batteries in series;
\item Number of batteries in parallel;
\item Autonomy of the batteries;
\item Efficiency from batteries;
\item Float, absorption, and bulk battery voltages;
\item Charge controller efficiency;
\item Charge controller current;
\item Charge controller maximum voltage;
\item Inverter output voltage;
\item Inverter AC reference power;
\item Inverter maximum (surge) AC power reference;
\item AC voltage (outlet standard);
\item Power demand from the house;
\item Surge demand from the house;
\item Energy consumption from the house.
\end{itemize}

Moreover, regarding the automated synthesis tool, it is necessary to add the following data (editing and modifying the code):

@@

%---------------------------------------
\subsection{Automated Verification with Incremental ESBMC}
%---------------------------------------

Here we describe precisely how to use the code explained in the previous section (\ref{sec:automatedverification}) using the incremental ESBMC with the Z3 SMT solver that presented the better performance during the comparative than other verifiers. However, in \ref{sec:setup} it was showed how to use the code with other verifiers.

@@

Some results issued by the ESBMC verifier were shown in \ref{sec:ESBMCverification} when performing the case studies.

%---------------------------------------
\subsection{Automated Synthesis with CPAchecker}
%---------------------------------------

Here we describe precisely how to use the code explained in previous sections (\ref{sec:automatedsynthesis}) using CPAchecker with MathSAT solver, which presented better performance during the comparative than other verifiers. However, in \ref{sec:synthesissetup} it was showed how to use the code with other verifiers.

@@

Install a Java Runtime Environment, which is at least Java 8 compatible (e.g., Oracle JRE, OpenJDK). Cf. the web site \url{http://java.oracle.com/}.

@@

Note that the default heap size is 1200m (or 1.2 GB of RAM). However, it is indicated to specify a significant value with '-heap' if you have more RAM available. In our case, we adjusted the heap to 64000m (64 GB).

Another important issue is the time-out of the execution process: the parameter 'limits.time.cpu' at the file 'resource-limits.properties' in folder 'config/includes' must be edited according to the desired value. In our case, 'limits.time.cpu = 14400s', i.e., 14400 seconds or 240 minutes or 4 hours.

Some results, reports, and graphics, issued by the CPAchecker verifier were depicted in \ref{sec:synthesisresults}.
